Bullet Groups as a test of $\Lambda$CDM

### 2014-02-27 paper/ms.tex
intro

\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\bullb}{MACS J0025.4-1222}
\newcommand{\bulla}{1E0657---56} 
\shorttitle{Bullet Groups}
\shortauthors{Fern\'andez-Trincado et al.}

@@

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.1\textwidth]{Figures_eps/figure_7_1.eps}
\end{center}
\caption{Cumulative distribution (P$>d_{2d,(X,Y)}$) of displacements
  for the projection (X,Y). {\bf Left panel:} Sample with
  $\nu_{max}>700$ kms$^{-1}$  for different redshifts. The vertical
  dashed line, correspond to the separation between dark matter to
  dark matter estimate in this work as the double of separation
  between the collisional gas and dark matter of 124$\pm$20 kpc
  reported by \citet{gastaldello} for the group SL2S J08544-0121.
  {\bf Right panel:} Sample with $300 $ kms$^{-1} <\nu_{max}<700 $
  kms$^{-1}$ for different redshifts.}  
\label{displacements}
\end{figure*}

@@

In order of estimate the number of Bullet Groups expected in the Bolshoi Cosmological Simulation, we 
define the configuration of this system as one where the substructure is coming out of the host halo ($cos(\theta)>0.5$). For this 
we make the scalar product between the velocity vector and position vector that defines the separation between 
 the host halo and the substructure, as shown below: \\

>>>>

\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}
\newcommand{\bullb}{MACS J0025.4-1222}
\newcommand{\bulla}{1E0657---56} 
\shorttitle{Bullet Groups}
\shortauthors{Fern\'andez-Trincado et al.}

@@

The Bullet Cluster provided a new kind of observational evidence of
the existece of dark matter. Quantifying the displacement between dark
matter and the dominant baryonic component (hot X-ray emitting gas)
has been used to test the CDM paradigm itself by quantifying the
substructure velocity requiered to produce such displacement and also
by estimating the expected abundance of such events in the Universe.

Since that time there are other observations of other Bullet-like
systems [...].

Recently \citep{Gastaldello} observed baryonic-DM displacement if
$124\pm 20$ kpc in a group-like system with a total mass $2.4\pm 0.6
\times 10^{14}$\Msun. Systems of this mass are $\sim 10$ times more massive
than cluster systems in the mass range $>10^{15}$\hMsun, this opens
up the possibility of observationally finding bullet groups in a fair
amount to impose constraints on $\Lambda$CDM. This greater abundance
has to be weighted by the fraction of systems that present large
displacements. Such study has been performed for clusters but not for
lower mass systems.

In this Letter we present prediction for the abundance of group-like
systems that might show a DM-baryon displacement. To this end we use a
N-body cosmological simulation with such a resolution that allows us
to identify multimodal dark matter clumps in the circular velocity
range $300-1000$\kms.

@@

\begin{figure*}
\begin{center}
%\includegraphics[width=1.1\textwidth]{Figures_eps/figure_7_1.eps}
\end{center}
\caption{Cumulative distribution (P$>d_{2d,(X,Y)}$) of displacements
  for the projection (X,Y). {\bf Left panel:} Sample with
  $\nu_{max}>700$ kms$^{-1}$  for different redshifts. The vertical
  dashed line, correspond to the separation between dark matter to
  dark matter estimate in this work as the double of separation
  between the collisional gas and dark matter of 124$\pm$20 kpc
  reported by \citet{Gastaldello} for the group SL2S J08544-0121.
  {\bf Right panel:} Sample with $300 $ kms$^{-1} <\nu_{max}<700 $
  kms$^{-1}$ for different redshifts.}  
\label{displacements}
\end{figure*}

@@

In order to estimate the number of Bullet Groups expected in the
Bolshoi Cosmological Simulation, we define the configuration of this system as one where the substructure is coming out of the host halo ($cos(\theta)>0.5$). For this 
we make the scalar product between the velocity vector and position vector that defines the separation between 
 the host halo and the substructure, as shown below: \\
